---
title: "Control_wells_dataexplore"
author: "Simon Marks"
date: "12/15/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(openair)
```

## Most Recent Compiled Data for Control- Nov 2020

```{r}

Control_wells_Nov2020 <- readr::read_csv("Control_Wells_Nov2020/raw/compiledwells_Control_Nov2020.csv", col_types = cols(Date = col_character(), .default = col_double())) %>% 
  dplyr::mutate(Date = as.POSIXct(Date, tz = "UTC"))

# filter out bad data, same technique for what was compiled into weekly averages

Control_wells_good_data_Nov2020 <- Control_wells_Nov2020 %>%
  dplyr::mutate(dplyr::across(starts_with("depth"), ~ case_when(
    . < 0 ~ 0,
    TRUE ~ .
  ))) %>% 
  dplyr::mutate(dplyr::across(starts_with("water"), ~ case_when(
    . <= 0.03 ~ 0,
    TRUE ~ .
  ))) %>% 
  # update depth to gw, resolving to well length when water level above sensor is 0
  dplyr::mutate(depth.gw_ft_CM0W = case_when(
    water.level.above.sensor_CM0W == 0 ~ 8.885,
    TRUE ~ depth.gw_ft_CM0W
  ), depth.gw_ft_CM1W = case_when(
    water.level.above.sensor_CM1W == 0 ~ 4.792,
    TRUE ~ depth.gw_ft_CM1W
  ), depth.gw_ft_CM2W = case_when(
    water.level.above.sensor_CM2W == 0 ~ 4.333,
    TRUE ~ depth.gw_ft_CM2W
  ), depth.gw_ft_CM3W = case_when(
    water.level.above.sensor_CM3W == 0 ~ 4.375,
    TRUE ~ depth.gw_ft_CM3W
  ), depth.gw_ft_CM4W = case_when(
    water.level.above.sensor_CM4W == 0 ~ 9.695,
    TRUE ~ depth.gw_ft_CM4W))

```

### Data for Plotting

```{r}

Control_wells_Nov2020_plots <- Control_wells_good_data_Nov2020 %>% 
  select(-starts_with("water")) %>% 
  tidyr::pivot_longer(cols = starts_with("depth"), names_to = "well_id", values_to = "depth_gw") %>% 
  dplyr::mutate(well_id = stringr::str_remove(well_id, "depth.gw_ft_")) %>% 
  dplyr::mutate(well_id = as.factor(well_id))

```

### CM0W

Notes:

* Data present 2019-04-24 16:30:00 to 2020-11-23 9:00:00

```{r}

CM0W_timeseries <- Control_wells_Nov2020_plots %>% 
  dplyr::filter(well_id == "CM0W") %>%
  # uncomment below line to customize date range plotted
  # dplyr::filter(Date > as.POSIXct("2019-9-25 00:00:00", tz = "UTC") & Date < as.POSIXct("2019-9-30 00:00:00", tz = "UTC")) %>% 
  ggplot(aes(x = Date, y = depth_gw)) +
  geom_line() +
  # adjust `date_breaks` argument below to adjust x-axis labels
  scale_x_datetime(date_labels = "%Y %b %d", date_breaks = "3 month")

CM0W_timeseries

```

### CM1W

Notes:

* Data present 2019-12-08 16:30:00 to 2020-11-23 09:00:00

```{r}

CM1W_timeseries <- Control_wells_Nov2020_plots %>% 
  dplyr::filter(well_id == "CM1W") %>%
  # uncomment below line to customize date range plotted
  # dplyr::filter(Date > as.POSIXct("2020-7-1 00:00:00", tz = "UTC") & Date < as.POSIXct("2020-7-14 00:00:00", tz = "UTC")) %>% 
  ggplot(aes(x = Date, y = depth_gw)) +
  geom_line() +
  # adjust `date_breaks` argument below to adjust x-axis labels
  scale_x_datetime(date_labels = "%Y %b %d", date_breaks = "3 month")

CM1W_timeseries

```

### CM2W

Notes:

* Data present 2019-12-08 18:00:00 to 2020-04-26 08:30:00
* CMW2 download moved water level to CMW4 deep well during April 2020, put in new well during July 2020 trip
* Data present 2020-07-07 18:30:00 to 2020-11-23 10:30:00

```{r}

CM2W_timeseries <- Control_wells_Nov2020_plots %>% 
  dplyr::filter(well_id == "CM2W") %>%
  # uncomment below line to customize date range plotted
  # dplyr::filter(Date > as.POSIXct("2020-7-1 00:00:00", tz = "UTC") & Date < as.POSIXct("2020-7-14 00:00:00", tz = "UTC")) %>% 
  ggplot(aes(x = Date, y = depth_gw)) +
  geom_line() +
  # adjust `date_breaks` argument below to adjust x-axis labels
  scale_x_datetime(date_labels = "%Y %b %d", date_breaks = "3 month")

CM2W_timeseries

```

### CM3W

Notes:

* Data present 2019-12-08 17:00:00 to 2020-11-23 10:30:00

```{r}

CM3W_timeseries <- Control_wells_Nov2020_plots %>% 
  dplyr::filter(well_id == "CM3W") %>%
  # uncomment below line to customize date range plotted
  # dplyr::filter(Date > as.POSIXct("2020-7-1 00:00:00", tz = "UTC") & Date < as.POSIXct("2020-7-14 00:00:00", tz = "UTC")) %>% 
  ggplot(aes(x = Date, y = depth_gw)) +
  geom_line() +
  # adjust `date_breaks` argument below to adjust x-axis labels
  scale_x_datetime(date_labels = "%Y %b %d", date_breaks = "3 month")

CM3W_timeseries

```

### CM4W

Notes:

* Dwyer set up was bad from Dec. 2019 to April 2020
* April 2020 Hobo from CM2W was moved here
* Data present 2020-04-26 11:30:00 to 2020-11-23 10:30:00

```{r}

CM4W_timeseries <- Control_wells_Nov2020_plots %>% 
  dplyr::filter(well_id == "CM4W") %>%
  # uncomment below line to customize date range plotted
  # dplyr::filter(Date > as.POSIXct("2020-7-1 00:00:00", tz = "UTC") & Date < as.POSIXct("2020-7-14 00:00:00", tz = "UTC")) %>% 
  ggplot(aes(x = Date, y = depth_gw)) +
  geom_line() +
  # adjust `date_breaks` argument below to adjust x-axis labels
  scale_x_datetime(date_labels = "%Y %b %d", date_breaks = "3 month")

CM4W_timeseries

```
