---
title: "RC_wells_dataexplore"
author: "Simon Marks"
date: "12/15/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(openair)
```

## Most Recent Compiled Data

#### Nov 2020 for CP wells, Sept 2019 for Plumas Corp

```{r}

RC_wells_Nov2020 <- readr::read_csv("RC_Wells_Nov2020/raw/compiledwells_RC_Nov2020.csv", col_types = cols(Date = col_character(), .default = col_double())) %>% 
  dplyr::mutate(Date = as.POSIXct(Date, tz = "UTC"))

plumas_corp_wells <- readr::read_csv("Plumas_Corp_Wells/compiledwells_RC_PlumasCorp_Sept2019.csv", col_types = cols(Date = col_character(), .default = col_double())) %>% 
  dplyr::mutate(Date = as.POSIXct(Date, tz = "UTC"))

# filter out bad data, same technique for what was compiled into weekly averages

RC_wells_good_data_Nov2020 <- RC_wells_Nov2020 %>%
  dplyr::mutate(dplyr::across(starts_with("depth"), ~ case_when(
    . < 0 ~ 0,
    TRUE ~ .
  ))) %>% 
  dplyr::mutate(dplyr::across(starts_with("water"), ~ case_when(
    . <= 0.03 ~ 0,
    TRUE ~ .
  ))) %>% 
  # update depth to gw, resolving to well length when water level above sensor is 0
  dplyr::mutate(depth.gw_ft_RCW1 = case_when(
    water.level.above.sensor_RCW1 == 0 ~ 9.508,
    TRUE ~ depth.gw_ft_RCW1
  ), depth.gw_ft_RCW2 = case_when(
    water.level.above.sensor_RCW2 == 0 ~ 4.626,
    TRUE ~ depth.gw_ft_RCW2
  ), depth.gw_ft_RCW3 = case_when(
    water.level.above.sensor_RCW3 == 0 ~ 8.622,
    TRUE ~ depth.gw_ft_RCW3
  ), depth.gw_ft_RCW6 = case_when(
    water.level.above.sensor_RCW6 == 0 ~ 9.508,
    TRUE ~ depth.gw_ft_RCW6
  ))

```

### Data for Plotting

```{r}
RC_wells_Nov2020_plots <- RC_wells_good_data_Nov2020 %>% 
  select(-starts_with("water")) %>% 
  tidyr::pivot_longer(cols = starts_with("depth"), names_to = "well_id", values_to = "depth_gw") %>% 
  dplyr::mutate(well_id = stringr::str_remove(well_id, "depth.gw_ft_")) %>% 
  dplyr::mutate(well_id = as.factor(well_id))

plumas_wells_plots <- plumas_corp_wells %>% 
  select(-starts_with("water")) %>% 
  tidyr::pivot_longer(cols = starts_with("depth"), names_to = "well_id", values_to = "depth_gw") %>% 
  dplyr::mutate(depth_gw = case_when(
    depth_gw < 0 ~ 0,
    TRUE ~ depth_gw
  )) %>% 
  dplyr::mutate(well_id = stringr::str_remove(well_id, "depth.gw_ft_")) %>% 
  dplyr::mutate(well_id = as.factor(well_id))
```

### RCW6

Notes:

* Data present 2019-05-30 15:00:00 to 2020-11-21 13:30:00
* Need to remove data on July 9- this was day slug test was done (anomaly in plot)


```{r}

RCW6_timeseries <- RC_wells_Nov2020_plots %>% 
  dplyr::filter(well_id == "RCW6") %>%
  # uncomment below line to customize date range plotted
  # dplyr::filter(Date > as.POSIXct("2019-9-25 00:00:00", tz = "UTC") & Date < as.POSIXct("2019-9-30 00:00:00", tz = "UTC")) %>% 
  ggplot(aes(x = Date, y = depth_gw)) +
  geom_line() +
  # adjust `date_breaks` argument below to adjust x-axis labels
  scale_x_datetime(date_labels = "%Y %b %d", date_breaks = "3 month")

RCW6_timeseries


```

### RCW3

Notes:

* Data present 2019-05-30 13:30:00 to 2019-12-16 02:30:00 (battery died powering system on Dwyer setup)
* Data present 2020-04-25 10:30:00 to 2020-11-21 13:30:00

```{r}

RCW3_timeseries <- RC_wells_Nov2020_plots %>% 
  dplyr::filter(well_id == "RCW3") %>%
  # uncomment below line to customize date range plotted
  # dplyr::filter(Date > as.POSIXct("2019-7-15 00:00:00", tz = "UTC") & Date < as.POSIXct("2019-7-30 00:00:00", tz = "UTC")) %>% 
  ggplot(aes(x = Date, y = depth_gw)) +
  geom_line() +
  # adjust `date_breaks` argument below to adjust x-axis labels
  scale_x_datetime(date_labels = "%Y %b %d", date_breaks = "3 month")

RCW3_timeseries

```
### RCW2

Notes:

* Data present 2019-09-03 11:00:00 to 2020-11-21 13:30:00
* water table only present between mid-April and early May in 2020, well is likely dry rest of time
* week of 2020-04-13 to 2020-04-20 is when the water table is closest to surface

```{r}

RCW2_timeseries <- RC_wells_Nov2020_plots %>% 
  dplyr::filter(well_id == "RCW2") %>%
  # uncomment below line to customize date range plotted
  # dplyr::filter(Date > as.POSIXct("2020-4-13 00:00:00", tz = "UTC") & Date < as.POSIXct("2020-4-16 00:00:00", tz = "UTC")) %>% 
  ggplot(aes(x = Date, y = depth_gw)) +
  geom_line() +
  # adjust `date_breaks` argument below to adjust x-axis labels
  scale_x_datetime(date_labels = "%Y %b %d", date_breaks = "3 month")

RCW2_timeseries

```

### RCW1

Notes:

* Data present 2019-05-31 07:30:00 to 2019-07-01 23:00:00 (problems with originally installed Dwyer instrument)
* Data present 2019-07-09 17:00:00 to 2019-10-21 17:30:00 (problems with originally installed Dwyer instrument)
* Data present 2019-12-09 12:00:00 to 2020-11-21 13:30:00 

```{r}

RCW1_timeseries <- RC_wells_Nov2020_plots %>% 
  dplyr::filter(well_id == "RCW1") %>%
  # uncomment below line to customize date range plotted
  # dplyr::filter(Date > as.POSIXct("2019-6-15 00:00:00", tz = "UTC") & Date < as.POSIXct("2019-6-20 00:00:00", tz = "UTC")) %>% 
  ggplot(aes(x = Date, y = depth_gw)) +
  geom_line() +
  # adjust `date_breaks` argument below to adjust x-axis labels
  scale_x_datetime(date_labels = "%Y %b %d", date_breaks = "3 month")

RCW1_timeseries

```

## RCW3P

Notes:

* Data present 2018-10-01 00:00:00 to 2019-09-30 23:45:00 (15 minute interval data)
* good looking diurnal pattern from groundwater data at Plumas wells, probably because of instrument quality

```{r}

RCW3P_timeseries <- plumas_wells_plots %>% 
  dplyr::filter(well_id == "RCW3P") %>%
  # uncomment below line to customize date range plotted
  # dplyr::filter(Date > as.POSIXct("2019-9-25 00:00:00", tz = "UTC") & Date < as.POSIXct("2019-9-30 00:00:00", tz = "UTC")) %>% 
  ggplot(aes(x = Date, y = depth_gw)) +
  geom_line() +
  # adjust `date_breaks` argument below to adjust x-axis labels
  scale_x_datetime(date_labels = "%Y %b %d", date_breaks = "3 month")

RCW3P_timeseries

```

## RCW4P

Notes:

* Data present 2019-02-08 02:15:00 to 2019-09-30 23:45:00 (15 minute interval data)
* good looking diurnal pattern from groundwater data at Plumas wells, probably because of instrument quality

```{r}

RCW4P_timeseries <- plumas_wells_plots %>% 
  dplyr::filter(well_id == "RCW4P") %>%
  # uncomment below line to customize date range plotted
  # dplyr::filter(Date > as.POSIXct("2019-9-25 00:00:00", tz = "UTC") & Date < as.POSIXct("2019-9-30 00:00:00", tz = "UTC")) %>% 
  ggplot(aes(x = Date, y = depth_gw)) +
  geom_line() +
  # adjust `date_breaks` argument below to adjust x-axis labels
  scale_x_datetime(date_labels = "%Y %b %d", date_breaks = "3 month")

RCW4P_timeseries

```