---
title: "Well_Processing_May2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Functions for processing

```{r}

source("well_processing_funs.R")

```
 
## Update RC Compilation

```{r}

## Prev RC Compile (Nov 2020)

RC_compile_Nov2020 <- readr::read_csv(file = "RC_Wells_Nov2020/raw/compiledwells_RC_Nov2020.csv", 
                                       col_types = cols(Date = col_character(), .default = col_double())) %>% 
  dplyr::mutate(Date = lubridate::ymd_hms(Date))

```

```{r}

# update the November RC well compilation 

RC_compile_May2021 <- process_well_data("RC_Wells_May2021/raw", site = "RC", prev_compile = RC_compile_Nov2020, written_file_name = "compiledwells_RC_May2021.csv")

```

## Update Control Compilation

```{r}

## Prev Control Compile (Nov 2020)

Control_compile_Nov2020 <- readr::read_csv(file = "Control_Wells_Nov2020/raw/compiledwells_Control_Nov2020.csv", 
                                       col_types = cols(Date = col_character(), .default = col_double())) %>% 
  dplyr::mutate(Date = lubridate::ymd_hms(Date))

```

```{r}

# update the November Control well compilation 
## Note: CM0W last measurement is erroneous because the logger took a measurement out of well

Control_compile_May2021 <- process_well_data("Control_Wells_May2021/raw", site = "control", prev_compile = Control_compile_Nov2020, written_file_name = "compiledwells_Control_May2021.csv")

```

## Update Marian Compilation

```{r}

## Prev Marian Compile (Nov 2020)

Marian_compile_Nov2020 <- readr::read_csv(file = "Marian_Wells_Nov2020/raw/compiledwells_Marian_Nov2020.csv", 
                                       col_types = cols(Date = col_character(), .default = col_double())) %>% 
  dplyr::mutate(Date = lubridate::ymd_hms(Date))

```

```{r}

Marian_compile_May2021 <- process_well_data("Marian_Wells_May2021/raw", site = "Marian", prev_compile = Marian_compile_Nov2020, written_file_name = "compiledwells_Marian_May2021.csv")

```

## Create Child's compilation

Notes:

* First creation of the Child's meadow compilation for wells "Childs_T2" and "Childs_T3"
* Child's well data was corrected in 'Childs_Wells_Nov2021/Baro_Correction/Nov2020_Childs_BaroCorrection.Rmd`, but was never formally compiled b/c didn't have well depths.
* Notice that because this was the first ever compile of Child's, we don't specify a file to append to. The nect compilation will append to the May 2021 compile done below.
* New barometric corrections were performed with R, due to extensive interpolation performed in HOBOware. 

```{r}

Childs_compile_May2021 <- process_well_data("Childs_Wells_May2021/raw", site = "Childs", written_file_name = "compiledwells_Childs_May2021.csv")

```

