---
title: "Control_Wells_weekly_avgs_Nov2020"
author: "Simon Marks"
date: "12/7/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(lubridate)
library(data.table)
library(openair)
```

## Latest Control Well Compilation Data (Nov 2020)

```{r}

Control_Wells_Nov2020 <- readr::read_csv("Control_Wells_Nov2020/raw/compiledwells_Control_Nov2020.csv", 
                                    col_types = cols(Date = col_character(), .default = col_double())) %>% 
  dplyr::mutate(Date = as.POSIXct(Date, tz = "UTC"))

```

## Data Q/C

* Compilation (previously done) procedure removes bad data (e.g. negative pressure values)
* This Q/C corrects:

1. The slight error associated with Dwyer well-setups (vented pressure transducers), where depth to groundwater resolved to a negative value when water table was in fact at the ground surface. Error is associated with PSI to water depth conversion for these wells.
2. Noise when wells are in fact dry. Typical error of U20 is 0.015 ft. Adjusts `water.level.above.sensor` vars and resolves `depth.gw` to the value of `well_length_ft - well_riser_ft` accordingly

```{r}

Control_Wells_good_data_Nov2020 <- Control_Wells_Nov2020 %>%
  dplyr::mutate(dplyr::across(starts_with("depth"), ~ case_when(
    . < 0 ~ 0,
    TRUE ~ .
  ))) %>% 
  dplyr::mutate(dplyr::across(starts_with("water"), ~ case_when(
    . <= 0.03 ~ 0,
    TRUE ~ .
  ))) %>% 
  # update depth to gw, resolving to well length when water level above sensor is 0
  dplyr::mutate(depth.gw_ft_CM0W = case_when(
    water.level.above.sensor_CM0W == 0 ~ 8.885,
    TRUE ~ depth.gw_ft_CM0W
  ), depth.gw_ft_CM1W = case_when(
    water.level.above.sensor_CM1W == 0 ~ 4.792,
    TRUE ~ depth.gw_ft_CM1W
  ), depth.gw_ft_CM2W = case_when(
    water.level.above.sensor_CM2W == 0 ~ 4.333,
    TRUE ~ depth.gw_ft_CM2W
  ), depth.gw_ft_CM3W = case_when(
    water.level.above.sensor_CM3W == 0 ~ 4.375,
    TRUE ~ depth.gw_ft_CM3W
  ), depth.gw_ft_CM4W = case_when(
    water.level.above.sensor_CM4W == 0 ~ 9.695,
    TRUE ~ depth.gw_ft_CM4W))
  
```

## Temporal Averaging Function

```{r}

temp_agg_meadow_dat <- function(data, start_day_of_week, interval = "30 min", avg.time = "7 day", data.thresh = 50, statistic = "mean"){
  
  # data <- readr::read_csv(path, col_types = cols(Date = col_character(), .default = col_double())) %>% 
  #   dplyr::mutate(Date = as.POSIXct(Date, tz = "UTC"))
  
  # path_write_out <- paste0(stringr::str_replace(path, "[^/]+$", replacement = ""), file_name_write)
  
  # Determine the dates corresponding to the first and last of chosen weekday (start date for averaging) present in data
  start_date <- data %>% 
    dplyr::mutate(is.chosen_wday = ifelse(lubridate::wday(Date) == start_day_of_week, T, F)) %>%
    dplyr::filter(is.chosen_wday == TRUE) %>% 
    dplyr::summarise(min(Date)) %>% 
    dplyr::pull()
  
  end_date <- data %>% 
    dplyr::mutate(is.chosen_wday = ifelse(lubridate::wday(Date) == start_day_of_week - 1, T, F)) %>%
    dplyr::filter(is.chosen_wday == TRUE) %>% 
    dplyr::summarise(max(Date)) %>% 
    dplyr::pull()
  
  data <- data %>% 
    # rename Date variable to "date" to play nicely w/ openair::timeAverage
    dplyr::rename(date = Date) %>% 
    dplyr::filter(date >= start_date & date <= end_date)
  
  aggregation <- openair::timeAverage(data, avg.time = avg.time, 
                                      data.thresh = data.thresh, statistic = statistic,
                                      start.date = start_date, end.date = end_date, interval = interval) %>% 
    # determine water year membership of the time avg- this might need to be tweaked
    dplyr::mutate(WY = dplyr::case_when(
      date %within% lubridate::interval(ymd("2017-10-01", tz = "UTC"), 
                                        ymd("2018-09-30", tz = "UTC")) ~ 2018,
      date %within% lubridate::interval(ymd("2018-10-01", tz = "UTC"), 
                                        ymd("2019-09-30", tz = "UTC")) ~ 2019,
      date %within% lubridate::interval(ymd("2019-10-01", tz = "UTC"), 
                                        ymd("2020-09-30", tz = "UTC")) ~ 2020,
      date %within% lubridate::interval(ymd("2020-10-01", tz = "UTC"), 
                                        ymd("2021-09-30", tz = "UTC")) ~ 2021,
    )) 
  # %>% 
  #   mutate(date = as.character(date)) %>% 
  #   rename(Date = date) %>%  
  #   # Write to .csv
  #   readr::write_csv(path = path_write_out)
  
}

```

## Weekly Averages for Control Well data

* First instruments at Control were well installed on September 13 of 2013 (Friday), so `start_day_of_week = 6`
* Maintains all other default arguments from above functions

**First week is week of 2019-04-26, last week is week of 2020-11-13**

```{r}

weekly_Control_Wells_toNov2020 <- temp_agg_meadow_dat(Control_Wells_good_data_Nov2020, interval = "30 min", start_day_of_week = 6) %>% 
  mutate(date = as.character(date)) %>%
  rename(Date = date) %>%
  dplyr::mutate(dplyr::across(starts_with("depth") | starts_with("water"), ~ round(., digits = 3)))

# write out to CSV

weekly_Control_Wells_toNov2020 %>% 
  readr::write_csv(path = "Control_Wells_Nov2020/weekly_Wells_Control_Nov2020.csv")


```
